\documentclass[11pt]{article}   % fleqn for left align of eqn
\usepackage{MyStyle}
\usepackage{blkarray}
\renewcommand\baselinestretch{1.0}\selectfont
\usepackage{enumerate}

\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}


\marginparwidth 0pt \oddsidemargin -2 truecm \evensidemargin  -2truecm \marginparsep -1pt \topmargin -3truecm \textheight 27truecm \textwidth 20 truecm


\def \HW {Assignment 1}
\def \courseCode {SEHH2241}
\def \dueTime {8 May (Fri) 11:59pm}

\begin{document}
\section*{\HW ~of \courseCode}
\begin{itemize}
	\item \textbf{Student Name (in English)}: $\rule{5cm}{0.15mm}$
	\item\textbf{Student ID}: $\rule{4cm}{0.15mm}$
	\item \textbf{Due date and time}: \dueTime .
\end{itemize}
\subsection*{Before attempting the assignment, please read the following carefully.}
\begin{itemize}
\item You must write your answers using the notations introduced in class.
\item Show all your steps clearly for all questions. 
% \item All your answers should be exact. If exact values cannot be obtained, round your final answers to four decimal places.
\item All your answers must be written in the the space provided.
\item Write your answers neatly. Unclear answers will not be marked.
\end{itemize}
\subsection*{Submission guidelines}
\begin{itemize}
\item \underline{SCAN} the ENTIRE assignment (including the front page) and saved it as ONE single PDF file. That is, even if you did not attempt some questions, you still need to scan that empty pages. Also, do not scan a portion of a page only---we need the ENTIRE page. 
\item Scan the assignment IN THE ORDER OF THE PAGES. That is, page 1 should come before page 2, and page 2 should come before page 3 and so on. 
\item Make sure that your work is properly scanned. Over-sized, blurred or upside-down pages will NOT be graded.
\item If you don’t have access to a scanner, you may use a mobile app (e.g., CamScanner) to scan it. The scanning by a physical scanner is preferable, though.  
\item You may use a tablet (e.g., Ipad) to write down your answers. However, you must ensure that your file can be opened using Adobe Reader on a Windows machine. If the file cannot be opened, no marks will be given. %In particular, \textbf{do not use the software \underline{Onenote} to do the assignment, because there will be difficulty printing out your assignment. }
\item You may type your solutions using a computer.
\item Upload the PDF and double check the integrity of your file. Sometimes the scanned file may appear differently on the Moodle system.
\item There is no requirement on the file name. 
\item Late submission, regardless of the reasons, will not be accepted. Submit your work to Moodle some time ahead of the deadline. Late submissions due to slow internet speed, for instance, will not be accepted.
\end{itemize}
\newpage
% \renewcommand\baselinestretch{1.0}\selectfont

% Q1
\begin{enumerate}[Q1.]
\item (xx pts)
\begin{enumerate}
\item 
\item 
\item 
\end{enumerate}
	\begin{solution}
	\newpage\phantom{xxx}
	\newpage\phantom{xxx}
	\end{solution}

% Q2
\item (xx pts)
\begin{enumerate}
\item 
\item 
\item 
\end{enumerate}
	\begin{solution}
	\newpage\phantom{xxx}
	\newpage\phantom{xxx}
	\end{solution}
% Q3
\item (xx pts)
\begin{enumerate}
% \item \fillwithlines{\fill}
\item 
\item 
\end{enumerate}
	\begin{solution}
	\newpage\phantom{xxx}
	\newpage\phantom{xxx}
	\end{solution}
% Q4
\item (xx pts)
\begin{enumerate}
\item 
\item 
\item 
\end{enumerate}
	\begin{solution}
	\newpage\phantom{xxx}
	\newpage\phantom{xxx}
	\end{solution}
% Q5
\item (xx pts)
\begin{enumerate}
\item 
\item 
\item 
\end{enumerate}
	\begin{solution}
	\newpage\phantom{xxx}
	\newpage\phantom{xxx}
	\end{solution}


\end{enumerate}
\end{document}





